Reproducibility in plant pathology: where do we stand and a way forward

### 2022-04-25 analysis/paper/paper.Rmd
insert linebreak between sentences for Rmd

Forty-eight articles scored 0% out of a possible 100% for reproducibility.
The mean value was 31.2% and the median value was 33.3%.
One article scored 100% or was classed as fully reproducible.
No journals surveyed were completely closed, all offered at least an option for open access but some were completely open.The majority of the articles were classed as fundamental, 160, with the remaining 138 classed as applied.

>>>>

Forty-eight articles scored 0% out of a possible 100% for reproducibility.
The mean value was 31.2% and the median value was 33.3%.
One article scored 100% or was classed as fully reproducible.
No journals surveyed were completely closed, all offered at least an option for open access but some were completely open.
The majority of the articles were classed as fundamental, 160, with the remaining 138 classed as applied.
